\documentclass[twocolumn]{aastex631}

\usepackage{amsmath}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{graphicx} 
\usepackage{aas_macros}

\begin{document}

In this paper, we have addressed the long-standing question of the physical origin of the algebraic degeneracy conditions required to ensure the stability of Higher-Order Scalar-Tensor (HOST) theories. These theories generically predict the existence of a catastrophic Ostrogradsky ghost instability, which is typically exorcised by imposing these conditions in an apparently ad-hoc manner. We have demonstrated that these conditions are not a mere mathematical contrivance but are instead the manifestation of a profound physical principle: an emergent gauge symmetry in the perturbative spectrum of the theory.

Our investigation focused on the dynamics of linear scalar perturbations around a Friedmann-Lema\^itre-Robertson-Walker cosmological background. By deriving the quadratic action for the two potentially propagating modes---the comoving curvature perturbation $\zeta$ and the scalar field fluctuation $\delta\phi$---we isolated the $2 \times 2$ kinetic matrix $\mathbf{K}$ that governs their stability. The central result of our work is the analytical proof that the determinant of this kinetic matrix is directly proportional to the algebraic expressions defining the degeneracy conditions. Consequently, imposing degeneracy is mathematically equivalent to enforcing the singularity of the kinetic matrix, $\det(\mathbf{K}) = 0$.

A singular kinetic matrix is the definitive signature of a redundancy in the system's degrees of freedom, which is the hallmark of a gauge symmetry. We made this symmetry explicit by constructing its associated gauge transformation. Upon imposing the degeneracy conditions, we solved for the null eigenvector of the singular kinetic matrix, which identifies the specific combination of perturbations that possesses no kinetic energy. We then defined a gauge transformation as a shift of the perturbation fields along this null direction and proved that the full quadratic action is invariant under this transformation.

This result provides a new and powerful physical interpretation of degeneracy. The would-be Ostrogradsky ghost is not a physical particle that is somehow projected out; rather, in a degenerate theory, it is revealed to be an unphysical, pure gauge degree of freedom from the outset. The degeneracy conditions are precisely the requirement for the emergence of a symmetry that renders this mode non-dynamical. This work thus establishes that the stability of viable HOST theories rests on a solid foundation of symmetry, transforming the degeneracy conditions from an algebraic prescription into a clear physical principle that ensures a consistent and healthy theory with a single propagating scalar degree of freedom.

\end{document}
                