\documentclass[twocolumn]{aastex631}

\usepackage{amsmath}
\usepackage{multirow}
\usepackage{natbib}
\usepackage{graphicx} 
\usepackage{aas_macros}

\begin{document}

A consistent quantization of Degenerate Higher-Order Scalar-Tensor (DHOST) theories is hindered by field-dependent gauge symmetries whose algebraic properties are poorly understood. We posit that these symmetries form an open algebra, which closes only upon use of the classical equations of motion, a structure that invalidates standard quantization methods and necessitates the Batalin-Vilkovisky (BV) formalism. We first confirm this by explicitly computing the commutator of infinitesimal gauge transformations to establish the open algebra's structure. We then construct the complete BV-extended action that correctly encodes this symmetry. The power of this framework is subsequently leveraged by employing the quantum master equation as a stringent consistency condition to constrain the form of permissible one-loop quantum corrections. This algebraic analysis reveals a powerful selection principle: it strictly forbids counter-terms built from the square of the Weyl tensor, while uniquely selecting a Gauss-Bonnet invariant. Remarkably, quantum consistency further fixes the coupling between the Gauss-Bonnet term and the scalar field to be a specific logarithmic function, whose parameters are inherited directly from the classical gauge transformation. This work demonstrates a profound and predictive link between a theory's classical open algebra and the definitive structure of its quantum corrections.

\end{document}
                